unbindall
bind quit kESCAPE
bind wpn_1 k1
bind wpn_2 k2
bind wpn_3 k3
bind wpn_4 k4
bind wpn_5 k5
bind wpn_6 k6
bind wpn_7 k7
bind wpn_8 k8
bind wpn_firemode_prev k9
bind wpn_firemode_next k0
bind scores kTAB
bind llookout kQ
bind forward kW
bind rlookout kE
bind wpn_reload kR
bind wpn_next kY
bind team_menu kU
bind inventory kI
bind skin_menu kO
bind active_jobs kP
bind crouch kLCONTROL
bind lstrafe kA
bind back kS
bind rstrafe kD
bind use kF
bind drop kG
bind contacts kH
bind torch kL
bind console kGRAVE
bind accel kLSHIFT
bind sprint_toggle kX
bind contacts kC
bind wpn_func kV
bind turn_engine kB
bind night_vision kN
bind map kM
bind chat kCOMMA
bind chat_team kPERIOD
bind jump kSPACE
bind cam_1 kF1
bind cam_2 kF2
bind cam_3 kF3
bind cam_4 kF4
bind vote_yes kF7
bind vote_no kF8
bind cam_zoom_out kSUBTRACT
bind cam_zoom_in kADD
bind screenshot kF12
bind pause kPAUSE
bind up kUP
bind left kLEFT
bind right kRIGHT
bind down kDOWN
bind wpn_fire mouse1
bind wpn_zoom mouse2
bind_console pause  kPAUSE
cam_inert 0.1
cam_slide_inert 0.25
cl_calculateping 0
cl_cod_pickup_mode 0
cl_dynamiccrosshair on
cl_leave_tdemo 0
cl_show_hit_sectors 1
cl_show_names 0
dbg_dump_physics_step 0
dbg_show_ani_info 0
g_always_run on
g_autopickup on
g_backrun on
g_checktime 0
g_corpsenum 10
g_eventdelay 0
g_game_difficulty stalker
g_gametask_auto_activate off
g_god on
g_unlimitedammo on
hud_animate_hit on
hud_crosshair on
hud_crosshair_dist off
hud_draw on
hud_fov 0.6
hud_info on
hud_news_disable 0
hud_weapon on
lua_gcstep 10
mouse_invert off
mouse_sens 0.2
mt_ai_vision on
mt_bullets on
mt_detail_path on
mt_level_path on
mt_object_handler on
mt_particles off
mt_script_gc on
mt_sound_player on
net_cl_icurvesize 0
net_cl_icurvetype 0
net_cl_inputguaranteed 0
net_cl_inputupdaterate 50
net_cl_interpolation 0.
net_cl_pending_lim 2
net_cl_update_rate 30
net_con_allowvoting off
net_con_damageblockindicator on
net_con_maprotation off
net_con_publicserver off
net_con_spectator 1
net_con_spectator_on off
net_dedicated_sleep 5
net_dump_size off
net_force_respawn 0
net_name Player
net_palyer_name DANGER
net_reinforcement 10
net_respawn_cur 0
net_respawn_damageblock 0
net_respawn_freezetime 5
net_srv_anomalytime 5
net_srv_artefactdelay 30
net_srv_artefactsnum 10
net_srv_artefactstay 0
net_srv_autoteambalance off
net_srv_dedicated off
net_srv_fraglimit 0
net_srv_friendlyfire 100
net_srv_friendlyindicators off
net_srv_gamemode Deathmatch
net_srv_maxplayers 32
net_srv_name user
net_srv_noanomalies off
net_srv_timelimit 0
net_srv_warmuptime 60
net_sv_control_hit 1
net_sv_pending_lim 2
net_sv_update_rate 30
net_weather_rateofchange 1
ph_break_common_factor 0.01
ph_fps 50
ph_gravity 19.62
ph_iterations 18
ph_rigid_break_weapon_factor 1.
ph_timefactor 1.
ph_tri_clear_disable_count 10
ph_tri_query_ex_aabb_rate 1.3
r1_dlights on
r1_dlights_clip 30.
r1_glows_per_frame 16
r1_lmodel_lerp 0.1
r1_pps_u 0.
r1_pps_v 0.
r1_ssa_lod_a 64.
r1_ssa_lod_b 48.
r1_tf_aniso 16
r1_tf_mipbias -3.
r2_aa on
r2_aa_break 0.000000,0.100000,0.000000
r2_aa_kernel 0.5
r2_aa_weight 0.250000,0.250000,0.000000
r2_allow_r1_lights on
r2_gi off
r2_gi_clip 0.001
r2_gi_depth 1
r2_gi_photons 16
r2_gi_refl 0.9
r2_ls_bloom_fast on
r2_ls_bloom_kernel_b 0.7
r2_ls_bloom_kernel_g 2.
r2_ls_bloom_kernel_scale 1.25
r2_ls_bloom_speed 10.
r2_ls_bloom_threshold 0.3
r2_ls_depth_bias -0.0001
r2_ls_depth_scale 1.00001
r2_ls_dsm_kernel 3.
r2_ls_psm_kernel 3.
r2_ls_squality 1.
r2_ls_ssm_kernel 0.7
r2_mblur 0.4
r2_parallax_h 0.05
r2_parallax_range 50.
r2_ssa_lod_a 96.
r2_ssa_lod_b 64.
r2_sun on
r2_sun_depth_far_bias 0.
r2_sun_depth_far_scale 1.
r2_sun_depth_near_bias -0.00004
r2_sun_depth_near_scale 1.00001
r2_sun_details on
r2_sun_focus on
r2_sun_lumscale 0.5
r2_sun_lumscale_amb 1.5
r2_sun_lumscale_hemi 0.
r2_sun_near 20.
r2_sun_near_border 0.77
r2_sun_tsm on
r2_sun_tsm_bias -0.05
r2_sun_tsm_proj 0.18
r2_tf_aniso 16
r2_tf_mipbias -3.
r2_tonemap on
r2_tonemap_adaptation 0.01
r2_tonemap_amount 0.
r2_tonemap_lowlum 0.001
r2_tonemap_middlegray 1.2
r2_zfill off
r2_zfill_depth 0.002
r2em 4.
r__geometry_lod 1.
r__geometry_lod_pow 1.5
r__lsleep_frames 10
r__ssa_glod_end 64.
r__ssa_glod_start 256.
r__supersample 4
r__wallmark_ttl 90.
recon_max_dist 50.
recon_max_speed 10.
recon_min_dist 2.
recon_min_speed 0.5
rs_c_brightness 1.
rs_c_contrast 1.
rs_c_gamma 1.
rs_constant_fps off
rs_fullscreen off
rs_ib_size 1024
rs_no_v_sync off
rs_occ_draw off
rs_occ_stats off
rs_refresh_60hz off
rs_render_dynamics on
rs_render_statics on
rs_skeleton_update 32
rs_stats off
rs_vb_size 1024
rs_vis_distance 1.
rs_warm_hzb off
snd_acceleration on
snd_cache_size 32
snd_efx on
snd_freq 44khz
snd_model High
snd_targets 32
snd_volume_eff 0.35459
snd_volume_music 0.64557
start_time_single 1.1.1 12:0:0.0
sv_bearercantsprint 1
sv_remove_corpse 1
sv_remove_weapon 1
sv_returnplayers 0
sv_shieldedbases 1
sv_statistic_collect 0
sv_statistic_save_auto 0
texture_lod 0
time_factor_single 10.
vid_bpp 32
vid_mode 1280x1024
